---
title: "LFXC_interval - behavioral results"
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    theme: default
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# About the code

Experiment: FXC_ILR
Version: TSS_LFXC20210602 --> probes every 3,4,5 intervals (36 efficacy probes)
Code written by: Ivan Grahek & Mahalia Prater Fahey
Description: Code for the analysis of behavioral data for the FXC_ILR project. This is an interval and garden task version of the LFXC task.  

\newpage

# Preprocessing

## Importing data
```{r, warning=FALSE, message=FALSE}
# Clear environment and import data

# clear the environment
rm(list=ls()) 
#load packages and install them if they're not installed
if (!require("pacman")) install.packages("pacman")
 pacman::p_load(plyr,Rmisc,yarrr,BayesFactor,reshape2,brms, broom, tidyverse, brmstools, BEST, knitr, here, zoo, magrittr, pracma,xtable, Hmisc, ppcor, lme4,MuMIn,MASS, sjPlot, jtools, lmerTest, sjstats,coefplot,R.matlab,RColorBrewer,cowplot,bayesplot,rstan,RColorBrewer,rstudioapi,corrplot,PCAmixdata,psych,rmarkdown,knitr,kable,mclust)

 # set seed
set.seed(42) 

# import
df.trial.combined=read.csv("Exp2Data_0.7Acc.csv")


```


# Main analyses

## Task Data Analysis (Trial-Based) 

### Accuracy - Model-based
```{r}
model.acc.trial1<-glmer(hit ~ mbased_efficacy_prev + mbased_reward_prev  + type + scaledIntervalLength   +scaledIntervalCong+
                   
                  (1 + mbased_efficacy_prev + type + mbased_reward_prev|uniqueid),
                data = df.trial.combined, family = binomial(link="logit"))

tab_model(model.acc.trial1,title = "Accuracy - Trial Based")

p = plot_model(model.acc.trial1,type = "pred", terms = "mbased_efficacy_prev")
p + theme_classic() + labs(x="Model-based efficacy estimate", y = "Accuracy")

p = plot_model(model.acc.trial1,type = "pred", terms = "type")
p + theme_classic() 

p = plot_model(model.acc.trial1,type = "pred", terms = c("mbased_efficacy_prev","type"))
p + theme_classic() 



p = coefplot(model.acc.trial1, intercept = FALSE, coefficients = c("mbased_efficacy_prev","mbased_reward_prev"))

p = p +  
  
  geom_vline(xintercept=0, linetype="dashed", color = "black") +
  
  labs(x = "Regression estimate") + 
  scale_x_continuous(limits = c(-1,1),breaks=seq(-1, 1, by = 0.2)) + 

  
  # ggtitle("Predicting reported efficacy\n") + 

  theme(axis.line = element_line(size=1, colour = "black"),
            panel.grid.major = element_line(colour = "grey",size = 0.1,linetype = "dashed"),
            panel.grid.minor = element_line(colour = "grey",size = 0.1,linetype = "dashed"),
              panel.border = element_blank(), 
              panel.background = element_blank(),
              plot.title = element_text(size = 18,  face = "bold",hjust = 0.5),
              text=element_text(colour="black", size = 14),
              axis.text.x=element_text(colour="black", size = 14),
              axis.text.y=element_text(colour="black", size = 14, face = "plain",hjust=0),
              axis.title=element_text(size=18,colour = "black",vjust = 1))

p

```






### Response Time - Model-based

```{r}



model.accrt.trial1<-lmer(log10_AccRT ~ mbased_efficacy_prev + type + mbased_reward_prev + scaledIntervalLength +  scaledIntervalCong+
                   
                  (1 + mbased_efficacy_prev  + type + mbased_reward_prev|uniqueid),
                data = df.trial.combined, REML = F)

tab_model(model.accrt.trial1,title = "RT - Trial Based")


p = plot_model(model.accrt.trial1,type = "pred", terms = "mbased_efficacy_prev")
p + theme_classic() + labs(x="Model-based efficacy estimate", y = "logRT")

p = plot_model(model.accrt.trial1,type = "pred", terms = "type")
p + theme_classic() 

p = plot_model(model.accrt.trial1,type = "pred", terms = c("mbased_efficacy_prev","type"))
p + theme_classic()



p = coefplot(model.accrt.trial1, intercept = FALSE, coefficients = c("mbased_efficacy_prev","mbased_reward_prev"))

p = p +  
  
  geom_vline(xintercept=0, linetype="dashed", color = "black") +
  
  labs(x = "Regression estimate") + 
  scale_x_continuous(limits = c(-0.07,0.03),breaks=seq(-0.07,0.03, by = 0.02)) + 

  
  # ggtitle("Predicting reported efficacy\n") + 

  theme(axis.line = element_line(size=1, colour = "black"),
            panel.grid.major = element_line(colour = "grey",size = 0.1,linetype = "dashed"),
            panel.grid.minor = element_line(colour = "grey",size = 0.1,linetype = "dashed"),
              panel.border = element_blank(), 
              panel.background = element_blank(),
              plot.title = element_text(size = 18,  face = "bold",hjust = 0.5),
              text=element_text(colour="black", size = 14),
              axis.text.x=element_text(colour="black", size = 14),
              axis.text.y=element_text(colour="black", size = 14, face = "plain",hjust=0),
              axis.title=element_text(size=18,colour = "black",vjust = 1))

p
```






